---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(tidyverse)
source("Table Summary.R")
source("First Chart/First Chart.R")
source("Second Chart.R")
source("Third Chart.R")
```
## Introductory Paragarph


## Summary Paragraph 


## Summary Table and Observations

### Summary Table
``` {r  echo = FALSE}
summary_table
```


## Charts

### Chart 1
``` {r  echo = FALSE}
heart_plot
```

### Chart 2
``` {r echo = FALSE}
chol_vs_restbp
```


### Chart 3
``` {r echo = FALSE}
bar_average
bar_count
```

The bar graph (bar_average) has the average amount of 
cholesterol levels for each type of chest pain. The other 
bar graph (bar_count) shows the frequency of each type of 
chest pain. The purpose of the first graph is to identify 
whether there a certain chest pain correlates with 
significantly high cholesterol levels. For this data set, 
all 4 chest pains had an average of similar cholesterol levels. 
Therefore, there was not a significant difference between 
types of chest pain and cholesterol levels. The bar_count 
graph can be used to verify that the data set is large 
enough and has enough samples to be considered reliable. 
3 of the chest pain types had well more than 100 cases; 
however, it is worth noting that TA had a relatively 
small sample size of cases (approximately 50). 
