---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(tidyverse)
source("Table Summary.R")
source("First Chart/First Chart.R")
source("Second Chart.R")
source("Third Chart.R")
```
## Introductory Paragarph


## Summary Paragraph 


## Summary Table and Observations

### Summary Table
``` {r  echo = FALSE}
summary_table
```


## Charts

### Chart 1
``` {r  echo = FALSE}
heart_plot
```

### Chart 2
``` {r echo = FALSE}
chol_vs_restbp
```

The line graph show the comparison of cholesterol level compared to the resting blood pressure. The purpose of this chart is too is identify the correlation of cholesterol and resting blood pressure. For this data set we found that cholesterol did not have a big correlation with resting blood pressure. Using the line chart we can see as the cholesterol changed the resting blood pressure stayed pretty consistent. The resting blood pressure ranged from about 100 - 200 but did not not depend on the cholesterol level of the patient.

### Chart 3
``` {r echo = FALSE}
bar_average
bar_count
```

The bar graph (bar_average) has the average amount of 
cholesterol levels for each type of chest pain. The other 
bar graph (bar_count) shows the frequency of each type of 
chest pain. The purpose of the first graph is to identify 
whether there a certain chest pain correlates with 
significantly high cholesterol levels. For this data set, 
all 4 chest pains had an average of similar cholesterol levels. 
Therefore, there was not a significant difference between 
types of chest pain and cholesterol levels. The bar_count 
graph can be used to verify that the data set is large 
enough and has enough samples to be considered reliable. 
3 of the chest pain types had well more than 100 cases; 
however, it is worth noting that TA had a relatively 
small sample size of cases (approximately 50). 
