---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(tidyverse)
source("Table Summary.R")
source("Summary Info.R")
source("First Chart/First Chart.R")
source("Second Chart.R")
source("Third Chart.R")
```

## Introductory Paragarph
The overarching theme for this analysis is health. While
in the midst of a pandemic, it's crucial to understand 
how to effectively maintain one's health and analyzing 
trends in health data sets can help individuals with this. 
These data sets provides insight into both physical and 
mental health as well as other health topics. The data sets
chosen focus on health related factors such as mental health, 
Covid/diet, and heart disease. These data sets can be 
utilized in order to answer questions such as is there 
correlations between age and cholesterol levels. In this 
case, the graphs created were primarily derived from the 
heart data set. 

For this analysis, we decided to focus on heart disease as cardiovascular diseases (CVDs) are the number 1 cause of death globally, taking an estimated 17.9 million lives each year. This dataset is made to help people with CVD help patients know if they have Cardiovascular disease before it’s too late. Data was collected by combining 5 different datasets which were Cleveland, Hungarian, Switzerland, Long Beach VA, Stalog (Heart) Data Set. In total there are 918 observations and 12 features in the dataset. This dataset can help answer our question about how


## Summary Paragraph 
_Write a summary paragraph that includes information calculated by your summary information function_



``` {r  echo = FALSE}
summary_info
```

## Aggregated Table and Observations
_Render your table and **describe pertinent observations** found in it_

We included this table to show the difference in health characteristics of those 
of the same age and  those who currently have and don't have a heart disease. The table is arranged by age and grouped to those who have or don't have a heart disease which is seen in the `HeartDisease` column where 0 represents the group without a  current heart disease and 1 representing those who do. The next few columns show the average resting blood pressure (`Avg_RestingBP`), average cholesterol (`Avg_Cholesterol`), and average maximum heart rate (`Avg_Max_HR`). We averaged and grouped these columns to show the difference in these health characteristics so that we can see how those of the same age but with different heart conditions differ. From this we found that depending on the age, these characteristics are all lower or higher, or some characteristics are lower or higher. From this, we can choose a specific age range to help predict heart disease based on these characteristics. 

``` {r  echo = FALSE}
summary_table
```


## Charts

### Chart 1
``` {r  echo = FALSE}
heart_plot
```

The graph shown below was used to demonstrate the correlation between age and resting bp. By using a scatter plot it is easier for the viewer to visualize the distribution of resting bp among the different ages. From the graph, you can see that as you get older there is no noticeable difference between the resting bp and the age with an exception of an outlier at age 70 where the resting bp is 0. 


### Chart 2
``` {r echo = FALSE}
chol_vs_restbp
```

The line graph show the comparison of cholesterol level compared to the resting blood pressure. The purpose of this chart is too is identify the correlation of cholesterol and resting blood pressure. For this data set we found that cholesterol did not have a big correlation with resting blood pressure. Using the line chart we can see as the cholesterol changed the resting blood pressure stayed pretty consistent. The resting blood pressure ranged from about 100 - 200 but did not not depend on the cholesterol level of the patient.

### Chart 3
``` {r echo = FALSE}
bar_average
bar_count
```

The bar graph (bar_average) has the average amount of 
cholesterol levels for each type of chest pain. The other 
bar graph (bar_count) shows the frequency of each type of 
chest pain. The purpose of the first graph is to identify 
whether there a certain chest pain correlates with 
significantly high cholesterol levels. For this data set, 
all 4 chest pains had an average of similar cholesterol levels. 
Therefore, there was not a significant difference between 
types of chest pain and cholesterol levels. The bar_count 
graph can be used to verify that the data set is large 
enough and has enough samples to be considered reliable. 
3 of the chest pain types had well more than 100 cases; 
however, it is worth noting that TA had a relatively 
small sample size of cases (approximately 50). 
